A few stickleback suffice to transport adaptive alleles to new lakes

### 2018-12-21 Stickleback_Paper.tex
latest edits

The canonical model for the genetics of adaptation, first formulated by Fisher in the early part of the 20th century, involves the sequential fixation of new mutations. 
While it has proven valid in numerous studies in the field as well as in the lab, this model is now rightfully understood as incomplete for many species in nature that have more complicated population structures. 
What role does genomic variation play in meta-populations with connection to an array of selective pressures?
How could migration-selection balance and ecological speciation actually benefit species as a whole?
A growing number of studies have identified instances of convergent or shared adaptive evolution in small demes that utilize standing genetic variation (SGV) found in the static population from which they split \citet{nelson2017ancient,Barrett2008,Schrider2017}.
However, it is still widely unknown which variations of evolutionary processes such as gene flow, recombination, selection and mutation, promote the maintenance and re-use of such genetic polymorphisms.
In addition, we would like to know how complex geographic systems, with a variety of selective pressures, interact with these evolutionary forces to help or hinder the use of SGV in newly colonized subpopulations.
\plr{I like the spirit of the first paragraph, but want to totally rewrite it}

@@

 \paragraph{Atmosphere's ability to carry whoever scotty is beaming up ... }
Perhaps the most notable finding in this study is that large, ancestral populations have the capacity to maintain alleles which are potentially deleterious for an extended amount of time.  
This principle, deriving solely from the properties of sex and natural selection, could be applicable to almost any species experiencing the influence of divergent selection with introgression.
And to explore further how this process is carried out exactly, many of the questions lie in understanding which properties of genomic architecture and demographics allow this transportation to be possible. 
his is largely analogous to exploring the specific properties of the atmosphere / space which allow for the heroes to be disassembled, then put back together.
In our simulations, the continued gene flow from freshwater populations meant that the alleles were maintained at a constant rate with fixed demographics. 
Two possible questions that might arise from this are:
(1) How do population sizes, demographics, and evolutionary histories impact an ancestral population's capacity for carrying maladaptive alleles in its opposing environment, and 
(2) What role does genomic architecture play in the ability for a haplotype to be rebuilt.

>>>>

The canonical model for the genetics of adaptation, first formulated by Fisher in the early part of the 20th century, involves the sequential fixation of new mutations. 
While it has proven valid in numerous studies in the field as well as in the lab, this model is now rightfully understood as incomplete for many species in nature that have more complicated population structures. 
What role does genomic variation play in meta-populations with connection to an array of selective pressures?
How could migration-selection balance and ecological speciation actually benefit species as a whole?
A growing number of studies have identified instances of convergent or shared adaptive evolution in small demes that utilize standing genetic variation (SGV) found in the static population from which they split \citet{nelson2017ancient,Schrider2017,Barrett2008}.
However, it is still widely unknown which variations of evolutionary processes such as gene flow, recombination, selection and mutation, promote the maintenance and re-use of such genetic polymorphisms.
In addition, we would like to know how complex geographic systems, with a variety of selective pressures, interact with these evolutionary forces to help or hinder the use of SGV in newly colonized subpopulations.
\plr{I like the spirit of the first paragraph, but want to totally rewrite it}

@@

 \paragraph{Atmosphere's ability to carry whoever scotty is beaming up ... }
Perhaps the most notable finding in this study is that large, ancestral populations have the capacity to maintain alleles which are potentially deleterious for an extended amount of time.  
This principle, deriving solely from the properties of sex and natural selection, could be applicable to almost any species experiencing the influence of divergent selection with introgression.
And to explore further how this process is carried out exactly, many of the questions lie in understanding which properties of genomic architecture and demographics allow this transportation to be possible. 
In our simulations, the continued gene flow from freshwater populations meant that the alleles were maintained at a constant rate with fixed demographics. 
Two possible questions that might arise from this are:
(1) How do population sizes, demographics, and evolutionary histories impact an ancestral population's capacity for carrying maladaptive alleles in its opposing environment, and 
(2) What role does genomic architecture play in the ability for a haplotype to be rebuilt.
